Deep Multimodal Generative Models for Weakly-Supervised Learning

### 2017-10-20 paper/draft.tex
added some background methods -- need to add description for MMVAE

\usepackage[utf8]{inputenc}
\usepackage[T1]{fontenc}
\usepackage{hyperref}
\usepackage{url}
\usepackage{booktabs}
\usepackage{amsfonts}
\usepackage{nicefrac}
\usepackage{microtype}
\usepackage{nips_2017}
\usepackage{natbib}
\setcitestyle{numbers,open={[},close={]}}

@@

\subsection{Related Work}
In deep learning, multimodal learning is often done using separate branches in the neural net for each modality, and a common top hidden layer. For instance, \citet{ngiam2011multimodal} trained deep autoencoders on audio and video input and found that the bimodal representations were better than any single equivalent. More recently, VAEs (\cite{kingma2013auto, kingma2014semi}) have been used to train models in high-dimensional multimodal settings. For example, conditional VAEs (\cite{sohn2015learning}) maximize a conditional log-likleihood by variational methods where often one modality is conditioned on another i.e. handwriting digits and labels, faces and attributes, or captioning. Notably, conditional VAEs (CVAE) are not bi-directional.

@@

\subsection{Variational Autoencoders}
\subsection{Product of Gaussians}
\subsection{Multimodal Variational Autoencoders}
\subsection{Bidirectional Inference}

>>>>

\usepackage[utf8]{inputenc}
\usepackage[T1]{fontenc}
\usepackage{hyperref}
\usepackage{url}
\usepackage{booktabs}
\usepackage{amsfonts}
\usepackage{nicefrac}
\usepackage{microtype}
\usepackage{nips_2017}
\usepackage{graphicx}
\usepackage{natbib}

\setcitestyle{numbers,open={[},close={]}}
\graphicspath{ {./images/} }

@@

\subsection{Related Work}
In deep learning, multimodal learning is often done using separate branches in the neural net for each modality, and a common top hidden layer. For instance, \citet{ngiam2011multimodal} trained deep autoencoders on audio and video input and found that the bimodal representations were better than any single equivalent. More recently, VAEs \cite{kingma2013auto, kingma2014semi} have been used to train models in high-dimensional multimodal settings. For example, conditional VAEs \cite{sohn2015learning} maximize a conditional log-likleihood by variational methods where often one modality is conditioned on another i.e. handwriting digits and labels, faces and attributes, or captioning. Notably, conditional VAEs (CVAE) are not bi-directional.

@@

\subsection{Variational Autoencoders}
Variational autoencoders (VAE) model a generative process as $z \sim \mathcal{N}(0, I)$ and $x \sim p_{\theta}(x | z)$ where $x$ is an observed variable, $z$ is a latent variable, and $\theta$ are the model parameters. VAE wish to maximize the marginal distribution $p(x) = \int p_{\theta}(x | z)p(z)dx$, which is intractor. Instead, we maximize the lower bound of the marginal distribution:

\begin{equation}
    \textup{log } p(x) \geq -D_{KL}(q_{\phi}(z | x) || p(z)) + E_{q_{\phi}}[\textup{log } p_{\theta}(x | z)]
\end{equation}

where $q_{\theta}(z | x)$ is a \textit{guide distribution} that approximates the posterior $p(z | x)$; $\theta$ are the parameters of $q$. In the text, we call $p_{\theta}(x | z)$ a decoder and $q_{\theta}(z | x)$ an encoder. In practice, $q$ is set to the familiy of Gaussian distributions, where optimization amounts to learning $\phi=\{\mu, \sigma\}$. The standard reparametrization trick is employed to sample $z$.

\subsection{Product of Experts}

We wish to model the interaction between our modalities as a product of experts. Fortunately, because our guide distributions are Gaussian, MMVAEs take advantage of the fact the product of two Gaussian distributions is itself a Gaussian distribution \cite{cao2014generalized}. The mean and covariance of the resulting Gaussian distribution is:

\begin{equation}
    \mu = (\sum_{i} \mu_{i}\Sigma^{-1}_{i})(\sum_{i}\Sigma^{-1}_{i})^{-1}
\end{equation}
\begin{equation}
    \Sigma = (\sum_{i} \Sigma^{-1}_{i})^{-1}
\end{equation}

where $\mu_{i}$, $\Sigma_{i}$ is the mean and covariance of the $i$-th Gaussian expert.

\subsection{Multimodal Variational Autoencoders}
\subsection{Bidirectional Inference}

\section{Experiments}
TODO
